Hybrid Threads for the Parrot Virtual Machine

### 2012-06-05 Paper.tex
Add more details about the usage of locks in the GC

Scheduling tasks on other interpreters may cause garbage collection due to the need of creating proxy objects. To protect the garbage collector from concurrency issues, garbage collection is disabled during creation of the new \textit{Task} object and the proxies on the target thread's \textit{interp}. But since the target thread may itself be allocating memory or collecting garbage, the GC has to be protected by a lock as well. The \textit{interp->thread\_data->interp\_lock} lock is used for this. It is checked by all allocation and freeing functions which are also the only places where a garbage collection run may be triggered.

>>>>

Scheduling tasks on other interpreters may cause garbage collection due to the need of creating proxy objects. To protect the garbage collector from concurrency issues, garbage collection is disabled during creation of the new \textit{Task} object and the proxies on the target thread's \textit{interp}. But since the target thread may itself be allocating memory or collecting garbage, the GC has to be protected by a lock as well. The \textit{interp->thread\_data->interp\_lock} lock is used for this. It is checked by all allocation and freeing functions which are also the only places where a garbage collection run may be triggered. Note that despite the GC being protected from concurrent access, this alone would still not be enough to share a GC between different threads since these threads could be changing references to objects while the GC does it's marking and sweeping. When only creating new proxies (which contain no references visible to the GC), accessing a foreign GC is safe on the other hand.
